---
title: "Figures"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,
                      fig.show='hide', 
                      warning=FALSE, 
                      message=FALSE,
                      tidy.opts = list(width.cutoff = 60),
                      tidy = TRUE)
```



```{r libraries, include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(imputeTS)
library(gt)
library(scales)
library(stringr)
library(readxl)
library(writexl)
library(gtExtras)
```

# Data
##Load Data
```{r}
study_data <- read_csv("study_data2.csv") 
diseasemodel_data <- read_csv("diseasemodel_data2.csv") 
outcome_data <- read_csv("outcome_data2.csv")
```

## My Data
```{r}
study_data <- study_data %>% 
  filter(Year>= 2018 & Year<= 2023, SystematicSearchName== "2020-2023 Update",
         InvestigatorName == "Laurel Renton", 
         StudyId != "6d537dfe-3d19-4dbf-b9af-bf9fad52bb4b")# this study was falsely included 

outcome_data <- outcome_data %>% 
  filter(Year>= 2018 & Year<= 2023, SystematicSearchName== "2020-2023 Update", 
         InvestigatorName == "Laurel Renton", 
         StudyId != "6d537dfe-3d19-4dbf-b9af-bf9fad52bb4b")

diseasemodel_data <- diseasemodel_data %>% 
  filter(Year>= 2018 & Year<= 2023, SystematicSearchName== "2020-2023 Update", 
         InvestigatorName == "Laurel Renton", 
         StudyId != "6d537dfe-3d19-4dbf-b9af-bf9fad52bb4b")
```

## Reporting Data 
```{r}
full_data_figures <- read.csv("full_data.csv") %>% 
    filter(AnnotatorIdStr == "00374321-95a7-4a2a-a12c-af4c0f9e599b",
           StudyId != "6d537dfe-3d19-4dbf-b9af-bf9fad52bb4b") %>% 
  select(StudyId) %>% 
  unique() %>% 
  mutate(other = 1)
```


## Number of Studies Included
```{r}
no_of_studies <- study_data %>% 
  filter(QuestionId == "335bd414-ce8b-4127-a4ff-b02ec66a3b81", Answer == "Yes")
```
24 studies included after the screening process. 

# Transgenic APP Models of AD 
## Data Wrangling
```{r}
diseasemodel_comments <- read_csv("comments.csv") %>% 
  filter(InvestigatorName == "Laurel Renton") %>% 
  select(StudyId, Answer, Comments) 
# adds comments for the models that weren't listed in the SyRF project


model_data <- diseasemodel_data %>% 
  left_join(diseasemodel_comments) %>% 
  filter(QuestionId =="8255f1cf-1db1-4756-b77c-003df2860ed9") %>% 
  select(StudyId, Answer, Comments) %>% 
  unique() %>%
  mutate(Answer = if_else(!is.na(Comments), Comments, Answer),
         Answer = str_replace_all(Answer,'AppNL-G-F', 'APP NL-G-F Knock-in'),
         Answer = str_replace_all(Answer, 'NL-P-F', 'APP NL-P-F Knock-in'), 
         Count = 1) %>% 
  select(Answer, Count) %>%
  group_by(Answer) %>% 
  summarise(Count = sum(Count)) %>% 
  filter(Answer != "PDGF-APP(WT) (line I5)")  
```

## Plotting Donut Plot
```{r}
# Donut plot
hsize <- 4

color_palette <- c("#D1E7F6","#75B6E5","#77CEEF","#1CADE4", "#2683C6", "#7AE0E5", "#42BA97", "#146266", "#A1C8C5", "#D3F5F6", "#BECAD4", "#597287", "#0E5772", "#134263", "#6E9281", "#59A79E")


donut_plot <- model_data %>%
  mutate(x = hsize) %>%
  ggplot(aes(x = hsize, y = Count, fill = Answer)) +
  geom_col(color = "black") +
  geom_text(aes(label = Count), position = position_stack(vjust = 0.5), size = 10,  color="white") +
  coord_polar(theta = "y") +
  scale_fill_manual(values = color_palette) +
  xlim(c(0.2, hsize + 0.5)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(), 
        legend.text=element_text(size=12)) +
  guides(fill = guide_legend(title = "AD APP Model"))
donut_plot
```


# Study Quality Protocols
```{r}
quality_data <- full_data_figures %>% 
  select(StudyId, `Sample Size` = "Is.a.sample.size.calculation.reported.",
         Blinding = "Does.the.paper.report.that.experimenters.were.blind.to.experimental.groups.during.outcome.assessment.",
         `Welfare Comitee Approval` = "Does.the.paper.report.that.experiments.were.approved.by.an.animal.welfare.committee",
         `Conflict of Interest` = "Is.there.a.conflicts.of.interest.statement.", 
         `Exclusion Criteria` = "Are.the.reasons.for.the.exclusion.of.data.points.reported.") %>% 
  unique() %>% 
  select(-StudyId) %>% 
  pivot_longer(cols = everything(), names_to = "study_quality_items", values_to = "Value") %>% 
  group_by(study_quality_items, Value) %>%
  summarize(Count = n()) %>%
  pivot_wider(names_from = Value, values_from = Count) %>% 
  mutate(overall = 23, 
         percentage_of_studies = `TRUE`/overall*100, 
         across(where(is.numeric), ~round(., 2))) 

quality_data_plot <- quality_data %>% 
  ggplot(aes(x=reorder(study_quality_items, -percentage_of_studies), y= percentage_of_studies))+
  geom_bar(stat="identity", fill="#174E77")+
  geom_text(aes(label=percentage_of_studies), position = position_dodge(width = .9), hjust= 1.25, color="white", size=3.5)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Studies (%) Reporting Different Study Quality Items")+
  labs(x = "Study Quality Items", y = "Included (%)")+
  coord_flip()+
  scale_y_continuous(labels = abs, limits = c(0, 100))

quality_data_plot
```

# Electrophysiology reporting quality
```{r, results="hide"}
## Applies to all experiments
ephys_data_1 <- full_data_figures %>% 
  filter(Outcome.category == "Electrophysiology") %>%
  select(StudyId, Outcome = "OutcomeLabel",
         Age = "What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.",
         `Brain Pathway` = "Brain.pathway.recorded",
         `Type of Recording Chamber` = "What.type.of.recording.chamber.was.used") %>% 
  unique() %>% 
  select(-c(StudyId, Outcome, Age)) %>% 
  mutate(`Brain Pathway` = "Reported",
         `Type of Recording Chamber` = case_when(`Type of Recording Chamber` == "Not reported"~"NotReported", 
                                TRUE~"Reported"))%>% 
  pivot_longer(cols = c(`Brain Pathway`, `Type of Recording Chamber`), names_to = "variable") %>%
  group_by(variable, value) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = value, values_from = count) %>% 
  na_replace(0) %>% 
  mutate(Overall = Reported+NotReported)


## Applies to only experiments looking at LTP and LTD
ephys_data_2 <- full_data_figures %>% 
  filter(Outcome.category == "Electrophysiology", 
         OutcomeLabel %in% c("LTP", "LTD")) %>%
  select(StudyId,
          Outcome = "OutcomeLabel",
         `Stimulation Type (LTP)` = "What.type.of.stimulation.was.used.to.induce.LTP.", 
         `Stimulation Type (LTD)` = "What.type.of.stimulation.was.used.to.induce.LTD.",
         Age = "What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.", 
         `Total Stimulations` = "Total.number.of.stimulations",
         `% of Maximal Response of Baseline Recording` = "Ephys..percentage.....of.maximal.response.from.input.output.used.for.baseline.recordings") %>% 
  unique() %>% 
  select(-StudyId, -Age) %>% 
  unite("Stimulation Type", c("Stimulation Type (LTP)", "Stimulation Type (LTD)")) %>% 
  mutate(`LTP/LTD Stimulation Type**`  = case_when(
    `Stimulation Type` == c("Other (please leave a comment)_", "_Other (please leave a comment)")~"NotReported",
                                    TRUE~"Reported"),
    `Total Stimulations**` = case_when(`Total Stimulations` == "NR"~"NotReported", TRUE~"Reported"), 
    `% of Maximal Response of Baseline Recording**` = case_when(`% of Maximal Response of Baseline Recording` == "NR"~"NotReported", TRUE~"Reported")) %>% 
  select(-c(Outcome, `Stimulation Type`)) %>% 
  pivot_longer(cols = c(`LTP/LTD Stimulation Type**`, `Total Stimulations**`, `% of Maximal Response of Baseline Recording**`), names_to = "variable") %>%
  group_by(variable, value) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = value, values_from = count)%>% 
  mutate(Overall = Reported+NotReported)

ephys_data <- ephys_data_1 %>% 
  full_join(ephys_data_2) %>% 
  mutate(percentage = Reported/Overall, 
          across(where(is.numeric), ~round(., 2))) %>% 
  select(-c(NotReported, Reported, Overall))


ephys_table <- ephys_data %>% 
  gt() %>%
  fmt_percent(columns = percentage, decimals = 1) %>% 
  tab_header(title = md("**Reporting Quality of Electrophysiology Measures**")) %>%
  cols_label(percentage = "Experiments Reported*") %>%
  tab_source_note(source_note = "* 58 experiments across 24 studies assessing synaptic plasticity/ transmission") %>%
  tab_source_note(source_note = "** across 28 experiments assessing LTP/LTD") %>% 
  tab_style(locations = cells_column_labels(columns = everything()),
            style = list(cell_borders(sides = "bottom", weight = px(3)),
                         cell_text(weight = "bold"))) %>% 
  cols_width(percentage~"70%")

ephys_table
```


# Animal Husbandary
```{r}
animal_data <- full_data_figures %>% 
  select(StudyId, lightcycle= "Animal.husbandry..light.cycle..h..of.animal.facilities", 
         animalspercage = "Animal.husbandry..number.of.animals.per.cage", 
         environmental = "Animal.husbandry..is.any.environmental.enrichment.reported.") %>% 
  unique() %>% 
  select(-StudyId) %>% 
  mutate(lightcycle = case_when(lightcycle == "NR"~"NotReported", TRUE~"Reported"), 
         animalspercage = case_when(animalspercage == "NR"~"NotReported", 
                                    TRUE~"Reported"), 
         environmental = case_when(environmental == "FALSE"~"NotReported", 
                                 TRUE~"Reported")) %>% 
  pivot_longer(cols = c(lightcycle, 
                        animalspercage,
                        environmental),
                        names_to = "variable") %>% 
  group_by(variable, value) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = value, values_from = count)%>% 
  mutate(Overall = Reported+NotReported, 
         percentage = Reported/Overall*100, 
         across(where(is.numeric), ~round(., 2))) %>% 
  select(-c(NotReported, Reported, Overall))
  
```


# Slice Protocol Measures
```{r}
slice_data <- full_data_figures %>% 
  select(StudyId,
         `Ca concentration in slicing solution` = "Ephys..calcium.concentration..mM..of.slicing.solution", 
         `Ca concentration in recording solution` = "Ephys..calcium.concentration..mM..of.recording.solution", 
         `Mg concentration in slicing solution` = "Ephys..magnesium.concentration..mM..of.slicing.solution", 
         `Mg concentration in recording solution` = "Ephys..magnesium.concentration..mM..of.ACSF.used.for.recording", 
         `Plane slice taken from` = "Which.plane.was.the.slice.taken.from.", 
         `Temperature slice left to recover at` = "Ephys..temperature...C..slices.left.to.recover.at", 
         `Slice recovery time` = "How.long..minutes..were.brain.slices.left.to.recover.after.slicing.",
         `Kynurenic acid used`= "Ephys..was.kynurenic.acid.used.during.the.brain.dissection.", 
         `Anaesthetised prior to sacrifice` = "Ephys..were.animals.anaesthetised.prior.to.decapitation.", 
         `Sacrifice time of day` = "Ephys..what.time.of.day.were.animals.sacrificed.") %>% 
  unique() %>% 
  select(-StudyId) %>% 
  mutate(`Ca concentration in slicing solution` = case_when(`Ca concentration in slicing solution` == "NR"~"NotReported", 
                                                              TRUE~"Reported"),
         `Ca concentration in recording solution` = case_when(`Ca concentration in recording solution` == "NR"~"NotReported", 
                                                              TRUE~"Reported"), 
         `Mg concentration in slicing solution` = case_when(`Mg concentration in slicing solution` == "NR"~"NotReported", 
                                                            TRUE~"Reported"), 
         `Mg concentration in recording solution` = case_when(`Mg concentration in recording solution` == "NR"~"NotReported", 
                                                            TRUE~"Reported"), 
         `Plane slice taken from` = case_when(`Plane slice taken from` == "Not reported"~"NotReported", TRUE~"Reported"),
         `Temperature slice left to recover at`= case_when(`Temperature slice left to recover at` == "NR"~"NotReported", 
                                                              TRUE~"Reported"), 
         `Slice recovery time` = case_when(`Slice recovery time` == "NR"~"NotReported", TRUE~"Reported"), 
         `Kynurenic acid used` = case_when(`Kynurenic acid used` == "No"~"NotReported", TRUE~"Reported"), 
         `Anaesthetised prior to sacrifice` = case_when(`Anaesthetised prior to sacrifice` == "Not reported"~"NotReported", 
                                TRUE~"Reported"),  
         `Sacrifice time of day` = case_when(`Sacrifice time of day` == "Not reported"~"NotReported", 
                                TRUE~"Reported"),)  %>% 
  pivot_longer(cols = c(`Ca concentration in slicing solution`,
                        `Ca concentration in recording solution`,
                        `Mg concentration in slicing solution`,
                        `Mg concentration in recording solution`,
                        `Plane slice taken from`,
                        `Temperature slice left to recover at`,
                        `Slice recovery time`,
                        `Kynurenic acid used`,
                        `Anaesthetised prior to sacrifice`, 
                        `Sacrifice time of day`),
                        names_to = "variable") %>% 
  group_by(variable, value) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = value, values_from = count)%>% 
  mutate(Overall = Reported+NotReported, 
         percentage = Reported/Overall*100, 
         across(where(is.numeric), ~round(., 2))) %>% 
  select(-c(NotReported, Reported, Overall)) 

slice_plot <- slice_data %>% 
  ggplot(aes(x= reorder(variable, percentage), y= percentage))+
  geom_bar(stat="identity", fill="#2683C6")+
  geom_text(aes(label=percentage), position = position_dodge(width = .9), hjust= 1.25, color="white", size=3.5)+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Studies(%) Reporing Different Slice Protocol Measures")+
  labs(x = "Protocol Measure", y = "Included (%)")+
  coord_flip()+
  scale_y_continuous(labels = abs, limits = c(0, 100))

slice_plot
```


# Age and Sex Data
```{r}
age_sex_data <- full_data_figures %>%
  filter(Outcome.category == "Electrophysiology") %>% 
  select(StudyId, Outcome = "OutcomeLabel", Age = "What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.", Sex = "Sex.of.animals.in.cohort") %>% 
  unique()
  

sex_data <- age_sex_data %>% 
  count(Sex) %>% 
  mutate(overall = sum(n), 
         percentage = n/ overall*100,  
         across(where(is.numeric), ~round(., 2))) %>% 
  ggplot(aes(x = Sex, y = percentage))+
  ylim(0, 100)+
  geom_bar(stat = "identity", fill = "#2683C6")+
  geom_text(aes(label=percentage), vjust = 1.5, color="white")+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Sex of Transgenic Animals Used")+
  labs(x = "Sex", y = "(%) Experiments Using Sex")

sex_data

age_count <- age_sex_data %>% 
  count(Age)

age_data <- age_sex_data %>% 
  mutate(Age = as.numeric(Age)) %>% 
  ggplot(aes(x=Age)) + 
  geom_histogram(aes(y=..density..), fill="#174E77")+
  theme(plot.title = element_text(hjust = 0.5))+
  ggtitle("Age of Transgenic Animals Used")+
  labs(x = "Age (Weeks)", y = "Density of Experiments Using Age")

age_data
```


# Publication Location
```{r}
countries_included <- full_data_figures %>% 
  select(region = "What.is.the.country.of.origin.of.the.corresponding.author", StudyId) %>% 
  unique() %>% 
  mutate(`Number of Studies` = 1) %>% 
  select(-StudyId) %>% 
  group_by(region) %>% 
  summarise(`Number of Studies` = sum(`Number of Studies`)) %>% 
  mutate(region = if_else(region == "United Kingdom", "UK",
                          if_else(region == "United States", "USA",
                                  if_else(region == "Korea, South", "South Korea", region))))


mapdata <- map_data("world") %>% 
  left_join(countries_included, by = "region") 

map1 <- mapdata %>% 
  ggplot(aes(x = long, y = lat, group = group)) + 
  geom_polygon(aes(fill = `Number of Studies`))
map1
```

# Year Published 
```{r}
year_data <- full_data_figures %>% 
  select(StudyId, Year) %>% 
  unique() %>% 
  mutate(`Number of Studies` = 1) %>% 
  select(-StudyId) %>% 
  group_by(Year) %>% 
  summarise(`Number of Studies` = sum(`Number of Studies`)) %>% 
  add_row(Year = 2023, `Number of Studies` = 0)

year_plot <- year_data %>% 
  ggplot(aes(x=Year, y= `Number of Studies`, group=1)) +
  geom_line()+
  geom_point()+
  geom_smooth(method = "lm", se= FALSE, col = "#174E77")

year_plot
```


## Publication Bias (I/O)
```{r}
# Define fill colors for contour
col.contour = c("gray75", "gray85", "gray95")

# Generate funnel plot (we do not include study labels here)
funnel.meta(ma_results_IO, xlim = c(-5, 5), #took the SMD from the forest plot
            contour = c(0.9, 0.95, 0.99),
            col.contour = col.contour)

# Add a legend
legend(x = -5, y = 0, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)

# Add a title
title("Funnel Plot of I/O")


## Adds columns to the ma_results_ltp30 to use in the Putejovsky analysis
ma_results_IO$n.e = IO_model_data_final$New_n_model
ma_results_IO$n.c = IO_model_data_final$`New_n_model control`

# Pustejovsky 
metabias(ma_results_IO, method.bias = "Pustejovsky")
```


## Trim and Fill (IO)
for outlier code https://raw.githubusercontent.com/MathiasHarrer/dmetar/master/R/find.outliers.R

```{r}
## Trim Fill
tf_IO <- trimfill(ma_results_IO)
summary(tf_IO)

## trim and fill is very sensitive to heterogeneity so a sensitivity test is carried out

## Test for outliers- sensitivity analysis
# if we remove outliers it reduces the heterogeneity and allows us to rerun the trim and fill
# find outliers 
find.outliers(ma_results_IO) ## have to load a package (chap 5.2 in handbook)

# filter out outliers and rerun meta and funnel plot
IO_nooutliers <- ma_results_IO %>% 
  filter(id != 10, 
         id != 5, 
         id != 3,
         id != 1) # needs to be checked when find the outliers

ma_results_IO_nooutliers <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experimen
  sm = "SMD",
  data = IO_nooutliers, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance

summary(ma_results_IO_nooutliers) ## reduces heterogenity to 25% 

tf_IO_nooutliers <- trimfill(ma_results_IO_nooutliers)
summary(tf_IO_nooutliers)


## plotting the two trim and fills
# Define fill colors for contour
contour <- c(0.9, 0.95, 0.99)
col.contour <- c("gray75", "gray85", "gray95")
ld <- c("p < 0.1", "p < 0.05", "p < 0.01")

# Use 'par' to create two plots in one row (row, columns)
par(mfrow=c(1,2))

# Contour-enhanced funnel plot (full data)
funnel.meta(tf_IO, 
            xlim = c(-5, 5), contour = contour,
            col.contour = col.contour)
legend(x = -5, y = 0, 
       legend = ld, fill = col.contour)
title("I/O Funnel Plot (Trim & Fill Method)")

# Contour-enhanced funnel plot (outliers removed)
funnel.meta(tf_IO_nooutliers, 
            xlim = c(-8, 8), contour = contour,
            col.contour = col.contour)
legend(x = -7.5, y = 0.01, 
       legend = ld, fill = col.contour)
title("Funnel Plot (Trim & Fill Method)
      -Outliers Removed", )
```


## MWM Check and data
```{r}
##Studies that include MWM and Ephys

MWM_data <- full_data %>% 
  filter(Outcome.category == "MWM") %>% 
  group_by(ExperimentID) %>% # within each StudyId and ExperimentId, filter to keep only cohorts with a model and model control row
  filter(any(ModelType == "model control") &
           any(ModelType == "model")) #%>% 
  #write_xlsx("MWM_data.xlsx")

```


# MWM Probe data
```{r}
MWM_probe <- read_xlsx("MWM_data.xlsx") %>% 
  filter(Type.of.MWM.outcome == "Probe phase")
  
MWM_probe_model <- MWM_probe %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, NumberOfAnimals, TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.MWM.outcomes.were.assessed.) %>% 
  mutate(TimeInMinute = "1") %>% 
  mutate(GreaterIsWorse = TRUE)

MWM_probe_model_data <- MWM_probe_model %>% 
  mutate(SD = ifelse(Outcome.measure.error.type == "SD", OutcomeError, OutcomeError * sqrt(NumberOfAnimals)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM", OutcomeError, SD / sqrt(NumberOfAnimals))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(NumberOfAnimals = as.numeric(NumberOfAnimals)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) 

MWM_probe_model_wide <- MWM_probe_model_data %>%
  pivot_wider(names_from = ModelType, values_from = c(NumberOfAnimals, SD, SEM, OutcomeResult, CohortId), values_fn=list) %>% 
  unnest(cols=everything()) 


MWM_probe_model_final <- MWM_probe_model_wide %>%
  mutate(combined_n = `NumberOfAnimals_model control` + NumberOfAnimals_model) %>%
  mutate(SPooled = sqrt(((`NumberOfAnimals_model control`- 1) * `SD_model control`^2 +
                           (NumberOfAnimals_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(NumberOfAnimals_model  * `NumberOfAnimals_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())

ma_results_MWM_probe <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experiment
  sm = "SMD",
  data = MWM_probe_model_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance
summary(ma_results_MWM_probe)


smd_MWM_probe <- ma_results_MWM_probe %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab") ## gets the SMD into a data frame

regression_MWM_probe <- MWM_probe_model_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_MWM_probe) # data set with SMD and SMD_ED, StudyId and id

```


# MWMW acquisition
```{r}
MWM_acquisition <- read_xlsx("MWM_data.xlsx") %>% 
  filter(Type.of.MWM.outcome == "Acquisition phase", 
         Was.this.a.visible.platform.test. != "TRUE") ## filter out visible
  
MWM_acquisition_model <- MWM_acquisition %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, NumberOfAnimals, TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.MWM.outcomes.were.assessed.) %>% 
  mutate(TimeInMinute = "1") %>% 
  mutate(GreaterIsWorse = TRUE)

MWM_acquisition_model_data <- MWM_acquisition_model %>% 
  mutate(SD = ifelse(Outcome.measure.error.type == "SD", OutcomeError, OutcomeError * sqrt(NumberOfAnimals)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM", OutcomeError, SD / sqrt(NumberOfAnimals))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(NumberOfAnimals = as.numeric(NumberOfAnimals)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) %>% 
  mutate(OutcomeLabel = "MWM acquisition")

MWM_acquisition_model_wide <- MWM_acquisition_model_data %>%
  pivot_wider(names_from = ModelType, values_from = c(NumberOfAnimals, SD, SEM, OutcomeResult, CohortId), values_fn=list) %>% 
  unnest(cols=everything())  ## error ask kaitlyn - cant pivot not sure why

# should run if pivot fixed
MWM_acquisition_model_final <- MWM_acquisition_model_wide %>%
  mutate(combined_n = `NumberOfAnimals_model control` + NumberOfAnimals_model) %>%
  mutate(SPooled = sqrt(((`NumberOfAnimals_model control`- 1) * `SD_model control`^2 +
                           (NumberOfAnimals_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(NumberOfAnimals_model  * `NumberOfAnimals_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())

ma_results_MWM_aquisition <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experiment
  sm = "SMD",
  data = MWM_acquisition_model_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance
summary(ma_results_MWM_aquisition)


smd_MWM_acquisition <- ma_results_MWM_aquisition %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab") ## gets the SMD into a data frame

regression_MWM_acquisition <- MWM_acquisition_model_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_MWM_acquisition) # data set with SMD and SMD_ED, StudyId and id
```


# Data for LTP at 30 mins
```{r}
# get the SMD into a data frame
smd_ltp30 <- ma_results_ltp30 %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab")

#get the SMD_ES into a data frame
regression_ltp30 <- LTP_model_data_30_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_ltp30)

```


# Data for LTP at 60 mins 
```{r}
smd_ltp60 <- ma_results_ltp60 %>% 
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab")

regression_ltp60 <- LTP_model_data_60_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_ltp60)
```

