---
title: "Meta-Analysis"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T,
                      fig.show='hide', 
                      warning=FALSE, 
                      message=FALSE,
                      tidy.opts = list(width.cutoff = 60),
                      tidy = TRUE, 
                      eval = FALSE)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
library(rmarkdown)
library(knitr)
library(janitor)
library(meta)
library(metafor)
library(readxl)
library(writexl)
```


## Full data wrangling
```{r}
full_data <- read.csv("full_data.csv") %>% 
    filter(AnnotatorIdStr == "00374321-95a7-4a2a-a12c-af4c0f9e599b", 
           NumberOfAnimals!= 0, #filters out studies with no n number
           StudyId != "6d537dfe-3d19-4dbf-b9af-bf9fad52bb4b")
```

#LTP data
## data wrangling to get the right data
```{r}
LTPdata <- full_data %>% 
  filter(Outcome.measure.category == "LTP")#%>% 
  #write_xlsx("newLTP_data.xlsx") # use this data to add n numbers

LTP_data <- read_xlsx("LTP_data_newn.xlsx") %>% 
  ## removes studies not needed
  group_by(ExperimentID) %>% 
  filter(any(ModelType == "model control") &
           any(ModelType == "model"))
```


```{r}
# selecting the right columns
LTP_model_data <- LTP_data %>% 
  select(MatchId, StudyId, 
         Author, OutcomeLabel,
         CohortId, ExperimentID,
         GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type,
         OutcomeError,
         Outcome.measure.error.type,
         ModelType, New_n, 
         TimeInMinute, 
         Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.)
```

## LTP 30 minutes 
```{r}
## LTP at 30 min
LTP_model_data_30 <- LTP_model_data %>% 
  filter(TimeInMinute >29 & TimeInMinute< 31) %>% # first look at LTP at 30 min 
  mutate(TimeInMinute = 30) %>%
  mutate(SD = ifelse(Outcome.measure.error.type == "SD",
                     OutcomeError, OutcomeError * sqrt(New_n)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM", 
                      OutcomeError, SD / sqrt(New_n))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(New_n = as.numeric(New_n)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) 
```

## Widen data set (30)
```{r}
LTP_model_data_30_wide <- LTP_model_data_30 %>%
  pivot_wider(names_from = ModelType,
              values_from = c(New_n, SD, SEM, OutcomeResult, CohortId),
              values_fn=list) %>% 
  unnest(cols=everything()) 
```


## Calculating effect sizes (30)
```{r}
LTP_model_data_30_final <- LTP_model_data_30_wide %>%
  mutate(combined_n = `New_n_model control` + New_n_model) %>%
  mutate(SPooled = sqrt(((`New_n_model control`- 1) * `SD_model control`^2 +
                           (New_n_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(New_n_model  * `New_n_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())
```


## Random effects meta-analysis (30)
```{r}
ma_results_ltp30 <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experiment
  sm = "SMD",
  data = LTP_model_data_30_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance

summary(ma_results_ltp30)
```


## Forest Plot (30)
```{r}
forest_plot_30 <- forest(
  ma_results_ltp30, # specify the meta-analysis to plot
  sortvar = TE, # sort the data according to effect size
  comb.fixed = FALSE, # do not plot the fixed effect estimate
  comb.random = TRUE, # plot the random effects estimate
  xlab = "SMD", # specify the x axis label
  smlab = "Standardised Mean Difference", # specify the effect size label
  label.right = "Increased LTP", # specify the graph label on right side of plot
  label.left = "Decreased LTP", # specify the graph label on left side of plot
  fontsize = 18, # specify the size of text (in points)
  plotwidth = "15cm", # specify the width of the plotting region
  digits = 1, # specify minimal number of significant digits for treatment effects
  digits.se = 1, # specify minimal number of significant digits for standard errors
  col.square="lightblue",
  leftcols = c("id"),
  leftlabs = c("id"),
  col.diamond = "darkblue",
  spacing=1.2
)
```


## Publication Bias (30)
```{r}
# Define fill colors for contour
col.contour = c("gray75", "gray85", "gray95")

# Generate funnel plot (we do not include study labels here)
funnel.meta(ma_results_ltp30, xlim = c(-8, 2), #took the SMD from the forest plot
            contour = c(0.9, 0.95, 0.99),
            col.contour = col.contour)

# Add a legend
legend(x = -7.5, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)

# Add a title
title("Funnel Plot of LTP after 30 min")


## Adds columns to the ma_results_ltp30 to use in the Putejovsky analysis
ma_results_ltp30$n.e = LTP_model_data_30_final$New_n_model
ma_results_ltp30$n.c = LTP_model_data_30_final$`New_n_model control`

# Pustejovsky 
metabias(ma_results_ltp30, method.bias = "Pustejovsky")


```

## Trim and Fill (30)
Needed to load to find outliers https://raw.githubusercontent.com/MathiasHarrer/dmetar/master/R/find.outliers.R
```{r}

## Trim Fill
tf_ltp30 <- trimfill(ma_results_ltp30)
summary(tf_ltp30)


# Define fill colors for contour
contour <- c(0.9, 0.95, 0.99)
col.contour <- c("gray75", "gray85", "gray95")
ld <- c("p < 0.1", "p < 0.05", "p < 0.01")

# Use 'par' to create two plots in one row (row, columns)
par(mfrow=c(1,2))

# Contour-enhanced funnel plot (full data)
funnel.meta(tf_ltp30, 
            xlim = c(-8, 8), contour = contour,
            col.contour = col.contour)
legend(x = -7.5, y = 0, 
       legend = ld, fill = col.contour)
title("Funnel Plot (Trim & Fill Method)")


# find outliers 
find.outliers(ma_results_ltp30) ## have to load a package (chap 5.2 in handbook)

# filter out outliers and rerun meta and funnel plot
ltp30_nooutliers <- LTP_model_data_30_final %>% 
  filter(id != 10, 
         id != 5, 
         id != 3)

ma_results_ltp30_nooutliers <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experimen
  sm = "SMD",
  data = ltp30_nooutliers, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance

summary(ma_results_ltp30_nooutliers) ## reduces heterogenity to 25% 

tf_ltp30_nooutliers <- trimfill(ma_results_ltp30_nooutliers)
summary(tf_ltp30_nooutliers)


# Define fill colors for contour
contour <- c(0.9, 0.95, 0.99)
col.contour <- c("gray75", "gray85", "gray95")
ld <- c("p < 0.1", "p < 0.05", "p < 0.01")


# Contour-enhanced funnel plot (outliers removed)
funnel.meta(tf_ltp30_nooutliers, 
            xlim = c(-8, 8), contour = contour,
            col.contour = col.contour)
legend(x = -7.5, y = 0.01, 
       legend = ld, fill = col.contour)
title("Funnel Plot (Trim & Fill Method)
      -Outliers Removed")

```



## LTP 60 minutes
```{r}
## LTP at 30 min
LTP_model_data_60 <- LTP_model_data %>% 
  filter(TimeInMinute >59 & TimeInMinute< 61) %>% # first look at LTP at 30 min 
  mutate(TimeInMinute = 60) %>%
  mutate(SD = ifelse(Outcome.measure.error.type == "SD",
                     OutcomeError, OutcomeError * sqrt(New_n)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM",
                      OutcomeError, SD / sqrt(New_n))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(New_n = as.numeric(New_n)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) 
```


## Widen data set(60)
```{r}
LTP_model_data_60_wide <- LTP_model_data_60 %>%
  pivot_wider(names_from = ModelType, values_from = c(New_n, SD, SEM,
                                                      OutcomeResult, CohortId), values_fn=list) %>% 
  unnest(cols=everything()) 
```


## Calculating effect sizes (60)
```{r}
LTP_model_data_60_final <- LTP_model_data_60_wide %>%
  mutate(combined_n = `New_n_model control` + New_n_model) %>%
  mutate(SPooled = sqrt(((`New_n_model control`- 1) * `SD_model control`^2 +
                           (New_n_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(New_n_model  * `New_n_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())
```

## Random effects meta-analysis (60)
```{r}
ma_results_ltp60 <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experimen
  sm = "SMD",
  data = LTP_model_data_60_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance

summary(ma_results_ltp60)
```

## Forest Plot (60)
```{r}
forest_plot_60 <- forest(
  ma_results_ltp60, # specify the meta-analysis to plot
  sortvar = TE, # sort the data according to effect size
  comb.fixed = FALSE, # do not plot the fixed effect estimate
  comb.random = TRUE, # plot the random effects estimate
  xlab = "SMD", # specify the x axis label
  smlab = "Standardised Mean Difference", # specify the effect size label
  label.right = "Increased LTP", # specify the graph label on right side of plot
  label.left = "Decreased LTP", # specify the graph label on left side of plot
  fontsize = 18, # specify the size of text (in points)
  plotwidth = "15cm", # specify the width of the plotting region
  digits = 1, # specify minimal number of significant digits for treatment effects
  digits.se = 1, # specify minimal number of significant digits for standard errors
  col.square="lightblue",
  leftcols = c("id"),
  leftlabs = c("id"),
  col.diamond = "darkblue",
  spacing=1.2
)
```


#I/O data
```{r}
IO_data <- full_data %>% 
  filter(OutcomeLabel == "I/O") #%>% 
  #write_xlsx("IO_data.xlsx")

IO_data <- read_xlsx("IO_data_newn.xlsx") %>% 
  group_by(ExperimentID) %>% 
  filter(any(ModelType == "model control") &
           any(ModelType == "model"))
```


```{r}
# selecting the right columns
IO_model_data <- IO_data %>% 
  select(MatchId, StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, New_n, TimeInMinute,
         Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.) %>% 
  mutate(TimeInMinute = "1")
```

## calculating SD and SEM 
```{r}
IO_model_data <- IO_model_data %>% 
  mutate(SD = ifelse(Outcome.measure.error.type == "SD", OutcomeError,
                     OutcomeError * sqrt(New_n)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM", 
                      OutcomeError, SD / sqrt(New_n))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(New_n = as.numeric(New_n)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) 
```

## Widen data set I/O
```{r}
IO_model_data_wide <- IO_model_data %>%
  pivot_wider(names_from = ModelType, 
              values_from = c(New_n, SD, SEM, OutcomeResult, CohortId),
              values_fn=list) %>% 
  unnest(cols=everything()) 
```


## Calculating effect sizes I/O
```{r}
IO_model_data_final <- IO_model_data_wide %>%
  mutate(combined_n = `New_n_model control` + New_n_model) %>%
  mutate(SPooled = sqrt(((`New_n_model control`- 1) * `SD_model control`^2 +
                           (New_n_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(New_n_model  * `New_n_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())
```


## Random effects meta-analysis I/O
```{r}
ma_results_IO <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experiment
  sm = "SMD",
  data = IO_model_data_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance

summary(ma_results_IO)


smd_IO <- ma_results_IO %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab") ## gets the SMD into a data frame
```


## Forest Plot I/O
```{r}
forest_plot_IO <- forest(
  ma_results_IO, # specify the meta-analysis to plot
  sortvar = TE, # sort the data according to effect size
  comb.fixed = FALSE, # do not plot the fixed effect estimate
  comb.random = TRUE, # plot the random effects estimate
  xlab = "SMD", # specify the x axis label
  smlab = "Standardised Mean Difference", # specify the effect size label
  label.right = "Increased I/O", # specify the graph label on right side of plot
  label.left = "Decreased I/O", # specify the graph label on left side of plot
  fontsize = 18, # specify the size of text (in points)
  plotwidth = "15cm", # specify the width of the plotting region
  digits = 1, # specify minimal number of significant digits for treatment effects
  digits.se = 1, # specify minimal number of significant digits for standard errors
  col.square="lightblue",
  leftcols = c("id"),
  leftlabs = c("id"),
  col.diamond = "darkblue",
  spacing=1.2
)
```

## Other Data needed
```{r}
PPF_data <- full_data %>% 
  filter(OutcomeLabel == c("PPF", "PPR")) %>% 
  group_by(ExperimentID) %>% 
  filter(any(ModelType == "model control") &
           any(ModelType == "model")) %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, Number.of.animals.in.cohort, 
         TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.) %>% 
  filter(TimeInMinute == "50")


LTP_90_data <- full_data %>% 
  filter(OutcomeLabel == "LTP") %>%
  group_by(ExperimentID) %>% 
  filter(any(ModelType == "model control") &
           any(ModelType == "model")) %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, Number.of.animals.in.cohort, 
         TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.) %>% 
  filter(TimeInMinute >89 & TimeInMinute< 91) %>% # first look at LTP at 30 min 
  mutate(TimeInMinute = 90)


LTD_30_data <- full_data %>% 
  filter(OutcomeLabel == "LTD") %>%
  group_by(ExperimentID) %>% 
  filter(any(ModelType == "model control") &
           any(ModelType == "model")) %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, Number.of.animals.in.cohort,
         TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.) %>% 
  filter(TimeInMinute >29 & TimeInMinute< 31) %>% # first look at LTP at 30 min 
  mutate(TimeInMinute = 30)

LTD_60_data <- full_data %>% 
  filter(OutcomeLabel == "LTD") %>%
  group_by(ExperimentID) %>% 
  filter(any(ModelType == "model control") &
           any(ModelType == "model")) %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, Number.of.animals.in.cohort,
         TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.EPhys.outcomes.were.assessed.) %>% 
  filter(TimeInMinute >59 & TimeInMinute< 61) %>% # first look at LTP at 30 min 
  mutate(TimeInMinute = 60)

```


## Publication Bias (I/O)
```{r}
# Define fill colors for contour
col.contour = c("gray75", "gray85", "gray95")

# Generate funnel plot (we do not include study labels here)
funnel.meta(ma_results_IO, xlim = c(-5, 5), #took the SMD from the forest plot
            contour = c(0.9, 0.95, 0.99),
            col.contour = col.contour)

# Add a legend
legend(x = -5, y = 0, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)

# Add a title
title("Funnel Plot of I/O")


## Adds columns to the ma_results_ltp30 to use in the Putejovsky analysis
ma_results_IO$n.e = IO_model_data_final$New_n_model
ma_results_IO$n.c = IO_model_data_final$`New_n_model control`

# Pustejovsky 
metabias(ma_results_IO, method.bias = "Pustejovsky")
```


## Trim and Fill (IO)
for outlier code https://raw.githubusercontent.com/MathiasHarrer/dmetar/master/R/find.outliers.R

```{r}
## Trim Fill
tf_IO <- trimfill(ma_results_IO)
summary(tf_IO)

## trim and fill is very sensitive to heterogeneity so a sensitivity test is carried out

## Test for outliers- sensitivity analysis
# if we remove outliers it reduces the heterogeneity and allows us to rerun the trim and fill
# find outliers 
find.outliers(ma_results_IO) ## have to load a package (chap 5.2 in handbook)

# filter out outliers and rerun meta and funnel plot
IO_nooutliers <- ma_results_IO %>% 
  filter(id != 10, 
         id != 5, 
         id != 3,
         id != 1) # needs to be checked when find the outliers

ma_results_IO_nooutliers <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experimen
  sm = "SMD",
  data = IO_nooutliers, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance

summary(ma_results_IO_nooutliers) ## reduces heterogenity to 25% 

tf_IO_nooutliers <- trimfill(ma_results_IO_nooutliers)
summary(tf_IO_nooutliers)


## plotting the two trim and fills
# Define fill colors for contour
contour <- c(0.9, 0.95, 0.99)
col.contour <- c("gray75", "gray85", "gray95")
ld <- c("p < 0.1", "p < 0.05", "p < 0.01")

# Use 'par' to create two plots in one row (row, columns)
par(mfrow=c(1,2))

# Contour-enhanced funnel plot (full data)
funnel.meta(tf_IO, 
            xlim = c(-5, 5), contour = contour,
            col.contour = col.contour)
legend(x = -5, y = 0, 
       legend = ld, fill = col.contour)
title("I/O Funnel Plot (Trim & Fill Method)")

# Contour-enhanced funnel plot (outliers removed)
funnel.meta(tf_IO_nooutliers, 
            xlim = c(-8, 8), contour = contour,
            col.contour = col.contour)
legend(x = -7.5, y = 0.01, 
       legend = ld, fill = col.contour)
title("Funnel Plot (Trim & Fill Method)
      -Outliers Removed", )
```


## MWM Check and data
```{r}
##Studies that include MWM and Ephys

MWM_data <- full_data %>% 
  filter(Outcome.category == "MWM") %>% 
  group_by(ExperimentID) %>% # within each StudyId and ExperimentId, filter to keep only cohorts with a model and model control row
  filter(any(ModelType == "model control") &
           any(ModelType == "model")) #%>% 
  #write_xlsx("MWM_data.xlsx")

```


# MWM Probe data
```{r}
MWM_probe <- read_xlsx("MWM_data.xlsx") %>% 
  filter(Type.of.MWM.outcome == "Probe phase")
  
MWM_probe_model <- MWM_probe %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, NumberOfAnimals, TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.MWM.outcomes.were.assessed.) %>% 
  mutate(TimeInMinute = "1") %>% 
  mutate(GreaterIsWorse = TRUE)

MWM_probe_model_data <- MWM_probe_model %>% 
  mutate(SD = ifelse(Outcome.measure.error.type == "SD", OutcomeError, OutcomeError * sqrt(NumberOfAnimals)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM", OutcomeError, SD / sqrt(NumberOfAnimals))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(NumberOfAnimals = as.numeric(NumberOfAnimals)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) 

MWM_probe_model_wide <- MWM_probe_model_data %>%
  pivot_wider(names_from = ModelType, values_from = c(NumberOfAnimals, SD, SEM, OutcomeResult, CohortId), values_fn=list) %>% 
  unnest(cols=everything()) 


MWM_probe_model_final <- MWM_probe_model_wide %>%
  mutate(combined_n = `NumberOfAnimals_model control` + NumberOfAnimals_model) %>%
  mutate(SPooled = sqrt(((`NumberOfAnimals_model control`- 1) * `SD_model control`^2 +
                           (NumberOfAnimals_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(NumberOfAnimals_model  * `NumberOfAnimals_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())

ma_results_MWM_probe <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experiment
  sm = "SMD",
  data = MWM_probe_model_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance
summary(ma_results_MWM_probe)


smd_MWM_probe <- ma_results_MWM_probe %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab") ## gets the SMD into a data frame

regression_MWM_probe <- MWM_probe_model_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_MWM_probe) # data set with SMD and SMD_ED, StudyId and id

```


# MWMW acquisition
```{r}
MWM_acquisition <- read_xlsx("MWM_data.xlsx") %>% 
  filter(Type.of.MWM.outcome == "Acquisition phase", 
         Was.this.a.visible.platform.test. != "TRUE") ## filter out visible
  
MWM_acquisition_model <- MWM_acquisition %>% 
  select(StudyId, Author, OutcomeLabel,
         CohortId, ExperimentID, GreaterIsWorse, OutcomeResult, 
         Outcome.measure.average.type, OutcomeError,
         Outcome.measure.error.type, ModelType, NumberOfAnimals, TimeInMinute, Sex.of.animals.in.cohort,
         What.age..weeks..were.animals.when.MWM.outcomes.were.assessed.) %>% 
  mutate(TimeInMinute = "1") %>% 
  mutate(GreaterIsWorse = TRUE)

MWM_acquisition_model_data <- MWM_acquisition_model %>% 
  mutate(SD = ifelse(Outcome.measure.error.type == "SD", OutcomeError, OutcomeError * sqrt(NumberOfAnimals)))%>% 
  mutate(SEM = ifelse(Outcome.measure.error.type == "SEM", OutcomeError, SD / sqrt(NumberOfAnimals))) %>%
  unique() %>% select(-OutcomeError) %>% # remove OutcomeError column 
  mutate(Direction= ifelse(GreaterIsWorse ==TRUE, 1, -1)) %>%
  mutate(NumberOfAnimals = as.numeric(NumberOfAnimals)) %>%
  mutate(OutcomeResult = as.numeric(OutcomeResult)) %>%
  mutate(SEM = as.numeric(SEM)) %>%
  mutate(SD = as.numeric(SD)) %>% 
  mutate(OutcomeLabel = "MWM acquisition")

MWM_acquisition_model_wide <- MWM_acquisition_model_data %>%
  pivot_wider(names_from = ModelType, values_from = c(NumberOfAnimals, SD, SEM, OutcomeResult, CohortId), values_fn=list) %>% 
  unnest(cols=everything())  ## error ask kaitlyn - cant pivot not sure why

# should run if pivot fixed
MWM_acquisition_model_final <- MWM_acquisition_model_wide %>%
  mutate(combined_n = `NumberOfAnimals_model control` + NumberOfAnimals_model) %>%
  mutate(SPooled = sqrt(((`NumberOfAnimals_model control`- 1) * `SD_model control`^2 +
                           (NumberOfAnimals_model - 1) * SD_model^2)/ (combined_n-2))) %>%
  mutate(SMD_step1 = (`OutcomeResult_model control`-`OutcomeResult_model`)
           /SPooled) %>%
  mutate(SMD_step2 = (1 - (3/(4*combined_n-9)))) %>%
  mutate(SMD_ES = SMD_step1 * SMD_step2 * Direction) %>% #equation 15
  mutate(SMD_ES_SE = sqrt(
    combined_n/(NumberOfAnimals_model  * `NumberOfAnimals_model control`) +
           SMD_ES^2/(2*(combined_n - 3.94)))) %>% #equation 16
  mutate(weight = 1/(SMD_ES_SE^2)) %>% #equation 20
  mutate(weighted_ES = SMD_ES * weight) %>% #equation 21 
  group_by(StudyId) %>%
  mutate(id = cur_group_id()) %>%
  select(id, everything())

ma_results_MWM_aquisition <- metagen(
  `SMD_ES`, # specify the effect size for each experiment
  `SMD_ES_SE`, # specify the variable that contains the standard error for each experiment
  sm = "SMD",
  data = MWM_acquisition_model_final, # specify the data set
  studlab = id, # specify the study labels
  comb.random = TRUE, # specify a random effects model
  comb.fixed = FALSE, 
  method.tau = "REML") # specify which method is used to estimate the between-study variance
summary(ma_results_MWM_aquisition)


smd_MWM_acquisition <- ma_results_MWM_aquisition %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab") ## gets the SMD into a data frame

regression_MWM_acquisition <- MWM_acquisition_model_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_MWM_acquisition) # data set with SMD and SMD_ED, StudyId and id
```


# Data for LTP at 30 mins
```{r}
# get the SMD into a data frame
smd_ltp30 <- ma_results_ltp30 %>%
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab")

#get the SMD_ES into a data frame
regression_ltp30 <- LTP_model_data_30_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_ltp30)

```


# Data for LTP at 60 mins 
```{r}
smd_ltp60 <- ma_results_ltp60 %>% 
  as.data.frame() %>% 
  select("SMD" = "TE", "id" = "studlab")

regression_ltp60 <- LTP_model_data_60_final %>% 
  select(SMD_ES, id, StudyId) %>% 
  left_join(smd_ltp60)
```


